---
title       : Developing Data Products - Course Project
subtitle    : Email - Spam or NonSpam
author      : Nami
job         : Lecturer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Introduction

This assignment uses data from Spam E-mail Detabase collected at Hewlett-Packard Labs, that classifies 4601 e-mails as spam or non-spam. 
In addition to this class label there are 57 variables indicating the frequency of certain words and characters in the e-mail. 

This shiny apps allows you to enter the frequency of some variables to predict if the mail is either "nonspam" or "spam".

--- .class #id 

## Data

The first 48 variables contain the frequency of the variable name (e.g., business) in the e-mail. If the variable name starts with num (e.g., num650) the it indicates the frequency of the corresponding number (e.g., 650). 
The variables 49-54 indicate the frequency of the characters ';', '(', '[', '!', '\$', and '#'. The variables 55-57 contain the average, longest and total run-length of capital letters. Variable 58 indicates the type of the mail and is either "nonspam" or "spam", i.e. unsolicited commercial e-mail.

--- 

## Classification Tree
Use the classification tree to find what variables can be used to determine the type of email (nonspam or spam).

```{r, echo=FALSE}
library(kernlab)
library(lattice)
library(ggplot2)
library(rpart)

data("spam")
index <- 1:nrow(spam)

set.seed(313)

testindex <- sample(index, trunc(length(index)/3))
testset <- spam[testindex,]
trainingset <- spam[-testindex,]

model.rpart <- rpart(type ~ ., method = "class", data = trainingset)

library(rattle)
plot(model.rpart, uniform = TRUE, main = "Classification (RPART). Classification Tree for SPAM")
text(model.rpart, all = TRUE, cex = 0.75)

```

--- 

## Predicting with Support Vector Machines model
Produce SVM model using the svm function. The SVM model is 90% accurate on the training data.
```{r echo=FALSE}
library(e1071)
model <- svm(type ~ ., data = trainingset, 
method = "C-classification", kernel = "radial", cost = 10, gamma = 0.1)
pred <- predict(model, testset)
library(caret)
confusionMatrix(pred,testset$type)
```
